2024 US Presidential Election Model

### 2024-10-20 paper/paper.qmd
committing rendered file

## Model set-up

## Model
Define \( y_i \) as the binary outcome variable indicating whether Donald Trump is predicted to win state \( i \) (1 if Trump wins, 0 if Harris wins). The predictor variables are \( \beta_i \), the average percentage of polling support for Donald Trump in state \( i \), and \( \gamma_i \), the average percentage of polling support for Kamala Harris in state \( i \).

\[
y_i|\mu_i \sim \text{Bernoulli}(\mu_i)
\]
\[
\mu_i = \alpha + \beta_i + \gamma_i
\]
\[
\alpha \sim \text{Normal}(0, 2.5)
\]
\[
\beta_i \sim \text{Normal}(0, 2.5)
\]
\[
\gamma_i \sim \text{Normal}(0, 2.5)
\]

>>>>

## Model set-up
Define \( y_i \) as the binary outcome variable indicating whether Donald Trump is predicted to win state \( i \) (1 if Trump wins, 0 if Harris wins). The predictor variables are \( \beta_i \), the average percentage of polling support for Donald Trump in state \( i \), and \( \gamma_i \), the average percentage of polling support for Kamala Harris in state \( i \).

\[
\begin{align}
y_i | \mu_i &\sim \text{Bernoulli}(\mu_i) \\
\mu_i &= \alpha + \beta_i + \gamma_i \\
\alpha &\sim \text{Normal}(0, 2.5) \\
\beta_i &\sim \text{Normal}(0, 2.5) \\
\gamma_i &\sim \text{Normal}(0, 2.5)
\end{align}
\]
